```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(tidyr)
library(plotly)
```

## Top dogs

In this homework, you will try to reproduce the fantastic infographic for [top dogs](https://informationisbeautiful.net/visualizations/best-in-show-whats-the-top-data-dog/), originally produced by David McCandless. The raw data can be found [here](https://docs.google.com/spreadsheets/d/1l_HfF5EaN-QgnLc2UYdCc7L2CVrk0p3VdGB1godOyhk/edit#gid=10). You can download this file by File -- Download As -- Microsoft Excel (.xlsx).

**Submission instructions**: Create a folder named `ds202_hw6`, and name the RMarkDown file including your solutions `hw6.Rmd` under this folder. For the submission, create a GitHub repository named `ds202_hw6` under your GitHub account, and push both `hw6.Rmd` and the knitted `hw6.html` before the deadline. I will assume you use the same GitHub username as for your HW5 submission. The latest version of your homework appearing on GitHub before the deadline is graded. *It is crucial to follow the exact folder structure and file names*, so that your homework can be reproduced and graded by an automated script. This homework is **due on April 22** before class.

1. Import the data and clean appropriately. To read in the data, you can use `readxl::read_xlsx('fileNameHere', sheet='sheetNameHere')`. Required data are in the sheets `Best in show` and `Best in show full sheet`. Take extra care on the column names and the first few rows of the data frame after read in.
```{r}
bestInShow <- readxl::read_xlsx('KIB.xlsx', sheet = 'Best in show')

bestInShowFull <- readxl::read_xlsx('KIB.xlsx', sheet = 'Best in show full sheet')

bestInShow <- bestInShow %>%
  select('Dog breed', 'popularity ranking (1-173, 1 = most popular)') 

names(bestInShow)[names(bestInShow) == 'popularity ranking (1-173, 1 = most popular)'] <- "Popular_Ranking"
names(bestInShow)[names(bestInShow) == 'Dog breed'] <- "Dog Breed"

bestInShowFull <- bestInShowFull %>%
  select('Dog Breed', 'category', 'datadog score', 'size category', 'intelligence category') %>%
  mutate('size category' = as.factor(bestInShowFull$'size category')) %>%
  mutate('intelligence category' = as.factor(bestInShowFull$'intelligence category')) %>%
  mutate(Intelligence = if_else(bestInShowFull$'intelligence category' == 'Lowest', 'Dumb', 'Clever')) %>%
  mutate(Intelligence = if_else(bestInShowFull$'intelligence category' == 'Fair', 'Dumb', 'Clever'))

bestInShowFull <- left_join(bestInShowFull, bestInShow, by = 'Dog Breed')

```

2. Create a graphics similar to the  [top dogs](https://informationisbeautiful.net/visualizations/best-in-show-whats-the-top-data-dog/) figure. Your figure needs to display the following information with appropriate plotting elements:

- breed of dog
- type of dog (work, toy, etc.)
- size of dog
- data score 
- popularity
- intelligence of the dog
- appropriate legends & explanation

```{r}
plot <- bestInShowFull %>%
  ggplot(aes(x = bestInShowFull$'datadog score', y = bestInShowFull$"Popular_Ranking", color = category, text = paste0("<b>Breed: </b>", bestInShowFull$'Dog Breed', "<br>", "<b>Size: </b>", bestInShowFull$'size category'))) +
  geom_point(aes(shape = bestInShowFull$'Intelligence')) +
  ##geom_text(aes(size = bestInShowFull$'size category', label = bestInShowFull$'Dog Breed'), nudge_y = -3) +
  scale_radius(range = c(2,3))+
  scale_y_reverse() +
  ggtitle("Replication of The Ultimate Data Dog") +
  xlab("Data Dog Score") +
  ylab("Popularity")

ggplotly(plot, tooltip = "text")

```

Hints and Notes:

- The breed of dog can be displayed without the silhouttes (text only is fine)
- Avoid (too much) overlaps!
- Choose a good color scheme.
- Your submission is supposed to be fully reproducible, i.e. the TA and I will 'knit' your submission in RStudio. 